BamSlicing
================
5/10/2023

## Installation instructions

## Inspect the available projects on GDC portal

#### Check ids for all the projects on GDC portal

```{r message=FALSE, warning=FALSE, echo='hide'}
library(BamSlicing)
availableProjectId()
```

#### Check the available Experimental Strategies give a project id.

```{r message=FALSE}
availableExpStrategy("TARGET-AML")
```

#### Check the available Workflows for each Experimental Strategies of a project.

```{r message=FALSE}
availableWorkFlow(projectId = "TARGET-AML", es = "RNA-Seq")
```

## Case Study

### Pediatric Acute Myeloid Leukemia (AML) onco-histone mutations
To investigate the genetic landscape of lysine-to-Methionine mutation at 27th animo acid of Histone 3 genes (H3K27M) in AML across ages, we examined 11 histone 3 genes as well as genes encoding epigenetic factors that are frequently mutated in AML patients (*IDH1/2*, *DNMT3A*, *RUNX1*, *ASXL1/2* and *TET1/2*). 

#### Query metadata of BAM files of Project on GDC
We can use availableProjectId(), availableExpStrategy() and availableWorkFlow() to find the keywords in order to get the information of BAM files on GDC portal. Here, we showed the example using TARGET-AML cohort with 2,281 subjects including 3,225 RNA-seq BAM files.

```{r message=FALSE}
file_meta = getGDCBAMs(projectId = "TARGET-AML", es = "RNA-Seq", workflow = "STAR 2-Pass Genome")
head(file_meta)
```