---
title: "Test fixIndelREfCounts by comparing with tallyReads."
author: "trichelab"
date: "06/25/2024"
output: github_document
---

```{r global_options}
knitr::opts_chunk$set(fig.path='Figs/test.fixIndeRefCounts')
```

### Missing Total read counts for INDELs in tallyreads() 
```{r message=FALSE,  warning=FALSE, echo='hide'}
library(bamSliceR)
demo_snp_02H053 -> demo_res
demo_res = system.file("data", "demo_tallyreads.rds", 
                            package = "bamSliceR")

demo_res = readRDS(demo_res)
INDEL_IDX = which(bamSliceR:::getVarType(demo_res) != "SNP")

summary(demo_res[INDEL_IDX]$VAF)
``` 


### Use fixIndelRefCounts to re-pileup on variants ranges###

```{r message=FALSE,  warning=FALSE, echo='hide'}
fixIndelRefCounts()
``` 

### Annotation of Variants ###
A VRanges object will be generated from tallying reads from BAM files, contains all the putative variants. sampleNames() can be used to see the name of BAM files which variants detected from. Here, We present an example on how to annotate variants with predicted consequence using [VariantAnnotation](https://bioconductor.org/packages/release/bioc/html/VariantAnnotation.html) and Ensembl Variant Effect Predictor ([VEP](https://useast.ensembl.org/info/docs/tools/vep/index.html)). 


```